$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-04 paper/paper.tex
Draft on Goto et al

Most of the work on mechanising resource-aware calculi is very recent.

@@

\cite{Goto2016a}
first session-type paper with a mechanised proof of type safety
Session types
Coq
Extrinisically typed
Session type polymorphism

@@

\cite{previous-work} polymorphic tokens, HOAS

>>>>

Considerable efforts in the mechanisation of resource-aware calculi have been made in recent years.

@@

The work by Goto et al. \cite{Goto2016a} is likely the first contribution to session-types that comes along with a mechanised proof of type safety (in Coq). 
Their paper extends session types with polymorphism and pattern matching on session types.
They use a locally-nameless encoding of variable references, a syntax prior to types, and a LTS semantics that encodes session-typed processes into the \picalc{}.
Their type system uses reorering of contexts and extrinsic contex splits.

@@
